Seismic Hazard Estimation of Northern Iran Using Smoothed Seismicity

### 2016-03-04 abstract.tex
additional fixes as agreed

% 
This article presents a seismic hazard assessment for northern Iran, where a smoothed seismicity approach has been used in combination with an updated seismic catalog and a ground motion prediction equation recently found to yield the best fit with data. We evaluate the hazard over a geographical area including the seismic zones of Azerbaijan, the Alborz Mountain Range, and Kopeh-Dagh. For completeness, we also consider the partial contribution of the seismic zones of Zagros to the southwest, and the south-central and southeastern Iranian seismic zones. In the chosen approach, seismic events are not assigned to specific faults but are instead assumed to be potential seismogenic sources by in themselves, and are spatially distributed within regular grid cells of size equal to 0.1\textdegree{} in both latitude and longitude. After performing the corresponding magnitude conversions, we decluster both historical and instrumental seismicity catalogs to obtain earthquake rates based on the number of events within each cell, and smooth the results to account for the uncertainty in the spatial distribution of future earthquakes. Seismicity parameters are calculated for each seismic zone separately, and for comparison purposes we also consider the combination of all zones into a single seismotectonic region. Seismic hazard curves are obtained for two distinct models defined based on the assumption that damage occurs above earthquake magnitude thresholds of $M_w$ greater than 4.5 and 5.0 for unreinforced and reinforced structures, respectively. We also obtain results for a combined scenario of these two models. The results are presented in terms of expected peak ground acceleration curves and hazard maps, considering exceedance probabilities of 2 and 10 percent in 50 years for rock site conditions. We compare our results to equivalent estimations available in the literature at selected locations and offer our perspective on the differences observed. In conclusion, we find our results to be helpful in understanding seismic hazard for northern Iran from a regional perspective, but highlight the fact that different methods may need to be combined to obtain more robust estimates at specific areas of interest.

>>>>

% 
This article presents a seismic hazard assessment for northern Iran, where a smoothed seismicity approach has been used in combination with an updated seismic catalog and a ground motion prediction equation recently found to yield the best fit with data. We evaluate the hazard over a geographical area including the seismic zones of Azerbaijan, the Alborz Mountain Range, and Kopeh-Dagh; and for completeness, we also consider the contribution of parts of other neighboring seismic zones that fall within our region of interest.
% For completeness, we also consider the partial contribution of the seismic zones of Zagros to the southwest, and the south-central and southeastern Iranian seismic zones. 
In the chosen approach, seismic events are not assigned to specific faults but are instead assumed to be potential seismogenic sources by in themselves, and are spatially distributed within regular grid cells of size equal to 0.1\textdegree{} in both latitude and longitude. After performing the corresponding magnitude conversions, we decluster both historical and instrumental seismicity catalogs to obtain earthquake rates based on the number of events within each cell, and smooth the results to account for the uncertainty in the spatial distribution of future earthquakes. Seismicity parameters are calculated for each seismic zone separately, and for comparison purposes we also consider the combination of all zones into a single seismotectonic region. Seismic hazard curves are obtained for two 
% distinct 
models defined based on the assumption that damage occurs above earthquake magnitude thresholds of $M_w$ greater than 4.5 and 5.0, depending on the type of construction, 
 % for unreinforced and reinforced structures, respectively. We 
and also obtain results for a combined scenario using these two models. The results are presented in terms of expected peak ground acceleration curves and hazard maps, considering exceedance probabilities of 2 and 10 percent in 50 years for rock site conditions. We compare our results to equivalent estimations available in the literature at selected locations and offer our perspective on the differences observed. In conclusion, we find our results to be helpful in understanding seismic hazard for northern Iran from a regional perspective, but highlight the fact that different methods may need to be combined to obtain more robust estimates at specific areas of interest.

### 2016-03-04 introduction.tex
additional fixes as agreed

Northern Iran houses nearly 40 percent (31.5 million) of the total population of the country in the cities of Tehran, Mashhad, Tabriz, Karaj, Qom, Orumieh, and Rasht. This region has suffered the devastating effects of earthquakes in the past \citep[e.g.,][]{Mehrain_1990_Tech, Chafory-Ashtiany_1999_DPM, Razzaghi_2012_Tech}. Due to its importance, northern Iran has recently been the subject of various efforts to better characterize seismic hazard in the region \citep[e.g.,][]{Abdollahzadeh2014a, Boostan2015}. In general, these studies highlight the significant seismic hazard of the region, and... \textcolor{red}{[need punch line conclusions here]}.

@@

In the following sections we describe in greater detail our region of interest, review the associated tectonics and seismicity, and provide additional information about the approach followed to estimate seismic hazard for the region. Significant aspects of our work include the composition of the earthquake catalog, including catalog completeness, the conversion of earthquake magnitudes, the selection of an appropriate attenuation relationship for the region \citep{Zafarani2014, Kalkan2004}, and the estimation of the Gutenberg-Richter seismicity parameters, which are necessary for the smoothed seismicity method. Our analysis includes seismic hazard curves and maps for peak ground acceleration considering exceedance probabilities of 2 and 10 percent in 50 years for rock site conditions. We consider two hazard models based on the assumption that damage occurs above earthquake magnitude thresholds of $M_w$ 4.5 and 5.0 for unreinforced and reinforced structures, respectively; and later combine these results into a single analysis based on the composition of the structural building inventory of the country. We compare our results to equivalent estimations (hazard curves) available in the literature for selected locations and conclude with a discussion in light of other previous hazard studies.

>>>>

Northern Iran houses about 41 percent (32 million) of the total population of the country in the cities of Tehran, Mashhad, Tabriz, Karaj, Qom, Orumieh, Rasht, and Ardabil. This region has suffered the devastating effects of earthquakes in the past \citep[e.g.,][]{Mehrain_1990_Tech, Chafory-Ashtiany_1999_DPM, Razzaghi_2012_Tech}. Due to its importance, northern Iran has recently been the subject of various efforts to better characterize seismic hazard in the region \citep[e.g.,][]{Abdollahzadeh2014a, Boostan2015}. Among other things, these studies have highlighted the prevailing differences between different studies, the importance of quantifying uncertainties, and the need for considering all potential faults in the region---even if believed inactive---by adopting new methodologies and the latest available data.

@@

In the following sections we describe in greater detail our region of interest, review the associated tectonics and seismicity, and provide additional information about the approach followed to estimate seismic hazard for the region. Significant aspects of our work include the composition of the earthquake catalog, including catalog completeness, the conversion of earthquake magnitudes, the selection of an appropriate attenuation relationship for the region \citep{Zafarani2014, Kalkan2004}, and the estimation of the Gutenberg-Richter seismicity parameters, which are necessary for the smoothed seismicity method. Our analysis includes seismic hazard curves and maps for peak ground acceleration considering exceedance probabilities of 2 and 10 percent in 50 years for rock site conditions. We consider two hazard models based on the assumption that damage occurs above an earthquake magnitude $M_w$ 4.5 for informal construction buildings, and above $M_w$ 5.0 for structures built in accordance to code regulations. The results of these two models are then combined 
% and 5.0 for unreinforced and reinforced structures, respectively; We later combine these results 
into a single analysis based on the composition of the structural building inventory of the country. We compare our results to equivalent estimations (hazard curves) available in the literature for selected locations and conclude with a discussion in light of other previous hazard studies.
